Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Mechanical Perturbations

### 2024-04-27 main.tex
Separate the eigenvalue figures and show stable regions.
Use the gain of -10 for the plot.

\todo[inline]{Show open loop bicycle rigid rider eigenvalue vs speed and then
the closed loop versions with the 8 and 10 gain settings. Three plots.}

\begin{figure}
  \centering
  \includegraphics{figures/balance-assist-controllers-eig-vs-speeds.png}
  \caption{Uncontrolled and controlled root locus of eigenvalue components
    plotted versus speed.}
  \label{fig:eigenvalues}
\end{figure}

>>>>

\begin{figure}
  \centering
  \subcaptionbox{}{
    \includegraphics[width=3in]{figures/uncontrolled-eig-vs-speeds.png}
  }
  \subcaptionbox{}{
    \includegraphics[width=3in]{figures/balance-assist-controllers-eig-vs-speeds.png}
  }
  \caption{Uncontrolled (a) and controlled (b) root locus of eigenvalue
    components (real: solid, imaginary: dashed) plotted versus speed. Vertical
    blue lines indicate the two speeds we perform experiments at. Green shaded
    region is the linear stable range.}
  \label{fig:eigenvalues}
\end{figure}
